\ieeetitle

### 2017-02-08 report/evaluation.tex
Fix figures and last typos

\subsection{Total GigaBytes sent/received}
This metric shows the total number of bytes sent and received on average during an experiment.
In all cases, \jgroups receives more bytes than it sends. This is due to the fact that we do not measure the bandwidth on the TCPGOSSIP, which is in charge of view changes. Thus, when a new peer joins the cluster, the TCPGOSSIP will send a new view to every peer already in the cluster.
\par
\begin{table}[hpt]
	\centering
	\caption{Total \si{\giga\byte} sent/received in a stable system}
	\sisetup{table-format=2.2, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
	\resizebox{\linewidth}{!}{
	\begin{tabular}{llSSS}
		\toprule
		&& \multicolumn{3}{c}{Cluster parameters} \\
		\cmidrule{3-5}
		{Protocol}&& {$(50,50)$} & {$(50,100)$} & {$(100,50)$} \\
		\midrule
		\multirow{2}{*}{\epto}&{Receive}& 10.84(016) & 22.31(039) & 26.01(027) \\
						    &{Sending}& 10.84(016) & 22.31(039) & 26.01(027)\\
		\midrule
		\multirow{2}{*}{\jgroups}&{Receive}& 0.78(003) & 1.45(001) & 1.88(001)\\
							   &{Sending}& 0.77(003) & 1.44(001) & 1.84(001)\\
		\bottomrule
	\end{tabular}
	}
	\label{table:total-bandwidth} 
\end{table}
In \autoref{table:total-bandwidth}, \epto has a worse baseline than \jgroups. This is expected as \epto sends $c*n*\log_2 n$ messages per events and \jgroups sends at least $n$ messages per event so we should have at least $c*\log_2 n$ more messages sent in \epto if \jgroups is perfect. Here we are well within this ratio.
\begin{table}[hpt]
	\centering
	\caption{Total \si{\giga\byte} sent/received with a synthetic churn}
	\sisetup{table-format=2.2, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
	\resizebox{\linewidth}{!}{
	\begin{tabular}{lSSS}
		\toprule
		&& \multicolumn{2}{c}{Churn parameters} \\
		\cmidrule{3-4}
		{Protocol}&& {1 kill/minute} & {1\{kill,add\}/minute} \\
		\midrule
		\multirow{2}{*}{\epto}&{Receive}& 21.00(024) & 26.32(032)\\
							&{Sending}& 21.21(025) & 26.57(032)\\
		\midrule
		\multirow{2}{*}{\jgroups-coord}&{Receive}& 1.47(002) & 1.75(002)\\&{Sending}& 1.43(002) & 1.70(002)\\
		\midrule
		\multirow{2}{*}{\jgroups-nocoord}&{Receive}& 1.45(001) & 1.73(002)\\&{Sending}& 1.41(001) & 1.68(002)\\
		\bottomrule
	\end{tabular}
	}
	\label{table:total-bandwidth-churn} 
\end{table}
In \autoref{table:total-bandwidth-churn} we see that \jgroups total bandwidth usage is smaller when there is churn. One hypothesis for this is that a \jgroups replica takes a longer time to start up compared to stopping a replica. Therefore the overall benchmark has a longer time with less than 100 replicas. We also do not see a difference whether we kill the coordinator or not. This can be explained by the fact that before the detection of a faulty coordinator \jgroups is forced to a halt for period of up to \SI{20}{\second} making the system unavailable. 
\subsection{Local Times}
\label{sub:local-times}
The local time represents the total time elapsed locally for a peer, between its first event sent and the last event it has delivered to the application.
 \begin{figure*}[hpt]
 	\centering
 	\includegraphics[width=\linewidth]{figures/local-times-nochurn.pdf}
 	\vspace{-2mm} 
 	\caption{Local dissemination times}
 	\vspace{-2mm}
 	\label{fig:local-times} 
 \end{figure*}

@@

\autoref{table:total-bandwidth-real-churn} also confirms our earlier results. \epto is still within the $c*log_2(n)$ ratio fixed earlier.

@@

When running \jgroups we sometimes get failed runs, where either some peers will experience holes or a peer will deliver out of order events. These failed runs only happen when there is churn happening, specifically when we add and remove peers and when the coordinator dies. These problems appeared 3 times out of 13 runs for \jgroups $1\{kill,add\}/minute$ and 2 times out of 7 for \jgroups with real churn. We have not investigated these problems further. This points to either \jgroups failing when there is too much churn or a bug present in the SEQUENCER implementation.

>>>>

\subsection{Total GigaBytes sent/received}
This metric shows the total number of bytes sent and received on average during an experiment.
In all cases, \jgroups receives more bytes than it sends. This is due to the fact that we do not measure the bandwidth on the TCPGOSSIP, which is in charge of view changes. Thus, when a new peer joins the cluster, the TCPGOSSIP will send a new view to every peer already in the cluster.
\par
\begin{table}[hpt]
	\centering
	\caption{Total \si{\giga\byte} sent/received in a stable system}
	\sisetup{table-format=2.2, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
	\resizebox{\linewidth}{!}{
	\begin{tabular}{llSSS}
		\toprule
		&& \multicolumn{3}{c}{Cluster parameters} \\
		\cmidrule{3-5}
		{Protocol}&& {$(50,50)$} & {$(50,100)$} & {$(100,50)$} \\
		\midrule
		\multirow{2}{*}{\epto}&{Receive}& 10.84(016) & 22.31(039) & 26.01(027) \\
						    &{Sending}& 10.84(016) & 22.31(039) & 26.01(027)\\
		\midrule
		\multirow{2}{*}{\jgroups}&{Receive}& 0.78(003) & 1.45(001) & 1.88(001)\\
							   &{Sending}& 0.77(003) & 1.44(001) & 1.84(001)\\
		\bottomrule
	\end{tabular}
	}
	\label{table:total-bandwidth} 
\end{table}
In \autoref{table:total-bandwidth}, \epto has a worse baseline than \jgroups. This is expected as \epto sends $c \cdot n \cdot \log_2 n$ messages per events and \jgroups sends at least $n$ messages per event so we should have at least $c  \cdot \log_2 n$ more messages sent in \epto if \jgroups is perfect. Here we are well within this ratio.
\begin{table}[hpt]
	\centering
	\caption{Total \si{\giga\byte} sent/received with a synthetic churn}
	\sisetup{table-format=2.2, separate-uncertainty, table-figures-uncertainty = 2, table-align-uncertainty}
	\resizebox{\linewidth}{!}{
	\begin{tabular}{lSSS}
		\toprule
		&& \multicolumn{2}{c}{Churn parameters} \\
		\cmidrule{3-4}
		{Protocol}&& {1 kill/minute} & {1\{kill,add\}/minute} \\
		\midrule
		\multirow{2}{*}{\epto}&{Receive}& 21.00(024) & 26.32(032)\\
							&{Sending}& 21.21(025) & 26.57(032)\\
		\midrule
		\multirow{2}{*}{\jgroups-coord}&{Receive}& 1.47(002) & 1.75(002)\\&{Sending}& 1.43(002) & 1.70(002)\\
		\midrule
		\multirow{2}{*}{\jgroups-nocoord}&{Receive}& 1.45(001) & 1.73(002)\\&{Sending}& 1.41(001) & 1.68(002)\\
		\bottomrule
	\end{tabular}
	}
	\label{table:total-bandwidth-churn} 
\end{table}
In \autoref{table:total-bandwidth-churn} we see that \jgroups total bandwidth usage is smaller when there is churn. One hypothesis for this is that a \jgroups replica takes a longer time to start up compared to stopping a replica. Therefore the overall benchmark has a longer time with less than 100 replicas. We also do not see a difference whether we kill the coordinator or not. This can be explained by the fact that before the detection of a faulty coordinator \jgroups is forced to a halt for period of up to \SI{20}{\second} making the system unavailable. 
\subsection{Local Times}
\label{sub:local-times}
The local time represents the total time elapsed locally for a peer, between its first event sent and the last event it has delivered to the application.
 \begin{figure*}[hpt]
 	\centering
 	\includegraphics[width=\linewidth]{figures/local-times-nochurn.pdf}
 	\vspace{-2mm} 
 	\caption{Local dissemination times}
 	\vspace{-2mm}
 	\label{fig:local-times} 
 \end{figure*}

@@

\autoref{table:total-bandwidth-real-churn} also confirms our earlier results. \epto is still within the $c \cdot log_2(n)$ ratio fixed earlier.

@@

When running \jgroups we sometimes get failed runs, where either some peers will experience holes or a peer will deliver out of order events. These failed runs only happen when there is churn happening, specifically when we add and remove peers and when the coordinator dies. These problems appeared 3 times out of 13 runs using the scenario and 2 times out of 7 for \jgroups following a real trace. We have not investigated these problems further. This points to either \jgroups failing when there is too much churn or a bug present in the SEQUENCER implementation.

### 2017-02-08 report/figures/architecture.tex
Correct typos in report
Fix figures and last typos

\begin{tikzpicture}[transform shape,scale=0.6]
\node[draw, text width=2.1cm, text centered] (bench) at (2.1, 2.6) {Benchmarks runner};
\draw (0.8,3.4) node[below right,red,scale=0.8] {\textit{Python script}};
\draw[dotted,red,thick] (0.8,2) rectangle (3.4,3.4);
%
\draw[loosely dashed,black] (3.7,4.3) rectangle (14.8,-0.8);
\draw (3.7,4.3) node[below right,black,scale=0.8] {\textit{Swarm overlay}};
%
\node[draw] (tck) at (12.4, 2.5) {Tracker};
\draw (11.6,3.25) node[below right,red,scale=0.8] {\textit{Python script}};
\draw (11.5,3.65) node[below right,blue,scale=0.8] {\textit{Service:} \texttt{epto-tracker:}};
\draw[loosely dashed,blue] (11.5,1.9) rectangle (14.5,3.65);
\draw[dotted,red,thick] (11.6,2) rectangle (14.4,3.25);
%
\draw[loosely dashed,blue] (4,-0.5) rectangle (10.8,3.65);
\draw (4,3.65) node[below right,blue,scale=0.8] {\textit{Service:} \texttt{epto}};
%
\node[draw] (app1) at (7.1, 2.5) {EpTOTester 1};
\draw (5.8,3.25) node[below right,red,scale=0.8] {\textit{Java program}};
\draw[dotted,red,thick] (5.8,2.1) rectangle (8.4,3.25);
%
\node[draw] (app2) at (5.4, 0) {EpTOTester 2};
\draw[dotted,red,thick] (4.1,-0.4) rectangle (6.7,.75);
%
\node[draw] (appn) at (9.4, 0) {EpTOTester N};
\draw[dotted,red,thick] (8.1,-0.4) rectangle (10.7,.75);
%
\draw[<->,thick,>=stealth] (app1.east) to[out=5,in=180] node[sloped,midway,scale=0.6,above]{HTTP} (tck.west);
\draw[<->,thick,>=stealth] (app2.east) to[out=55,in=180] node[sloped,midway,scale=0.6,above]{HTTP} (tck.west);
\draw[<->,thick,>=stealth] (appn.east) to[out=5,in=180] node[sloped,midway,scale=0.6,above]{HTTP} (tck.west);
%
\draw[->,thick,>=stealth] (bench.east) to[out=5,in=180] node[sloped,midway,scale=0.6,above]{Docker API calls} (4,1);
%
\draw[<->,thick,>=stealth] (app1.south) -- node[sloped,midway,scale=0.6,above]{UDP} (app2.north);
\draw[<->,thick,>=stealth] (app1.south) -- node[sloped,midway,scale=0.6,above]{UDP} (appn.north);
\draw[<->,thick,>=stealth] (app2.east) -- node[sloped,midway,scale=0.6,above]{UDP} (appn.west);
%
\draw (8.1,.75) node[below right,red,scale=0.8] {\textit{Java program}};
\draw (4.1,.75) node[below right,red,scale=0.8] {\textit{Java program}};
\end{tikzpicture}

>>>>

\begin{tikzpicture}[transform shape,scale=0.6]
\node[draw, text width=2.1cm, text centered] (bench) at (2.1, 2.6) {Benchmarks runner};

\draw (0.8,2.05) node[below right,red,scale=0.8] {\textit{LSDSuite module}};
\draw[red] (0.9,0.1) rectangle (3.3,2.05);
\node[draw, text width=2cm, text centered] (churnc) at (2.1,1.4) {Churn Class};
\node[draw, text width=2cm, text centered] (benchc) at (2.1, 0.6) {Benchmark Class};
\draw (0.8,3.4) node[below right,red,scale=0.8] {\textit{Python scripts}};
\draw[dotted,red,thick] (0.8,0) rectangle (3.4,3.4);
%
\draw[loosely dashed,black] (3.7,4.3) rectangle (14.8,-0.8);
\draw (3.7,4.3) node[below right,black,scale=0.8] {\textit{Swarm overlay}};
%
\node[draw] (tck) at (12.4, 2.5) {Tracker};
\draw (11.6,3.25) node[below right,red,scale=0.8] {\textit{Python script}};
\draw (11.5,3.65) node[below right,blue,scale=0.8] {\textit{Service:} \texttt{epto-tracker}};
\draw[loosely dashed,blue] (11.5,1.9) rectangle (14.5,3.65);
\draw[dotted,red,thick] (11.6,2) rectangle (14.4,3.25);
%
\draw[loosely dashed,blue] (4,-0.5) rectangle (10.8,3.65);
\draw (4,3.65) node[below right,blue,scale=0.8] {\textit{Service:} \texttt{epto}};
%
\node[draw] (app1) at (7.1, 2.5) {EpTOTester 1};
\draw (5.8,3.25) node[below right,red,scale=0.8] {\textit{Java program}};
\draw[dotted,red,thick] (5.8,2.1) rectangle (8.4,3.25);
%
\node[draw] (app2) at (5.4, 0) {EpTOTester 2};
\draw[dotted,red,thick] (4.1,-0.4) rectangle (6.7,.75);
%
\node[draw] (appn) at (9.4, 0) {EpTOTester N};
\draw[dotted,red,thick] (8.1,-0.4) rectangle (10.7,.75);
%
\draw[<->,thick,>=stealth] (app1.east) to[out=5,in=180] node[sloped,midway,scale=0.6,above]{HTTP} (tck.west);
\draw[<->,thick,>=stealth] (app2.east) to[out=55,in=180] node[sloped,midway,scale=0.6,above]{HTTP} (tck.west);
\draw[<->,thick,>=stealth] (appn.east) to[out=5,in=180] node[sloped,midway,scale=0.6,above]{HTTP} (tck.west);
%
\draw[->,thick,>=stealth] (bench.east) to[out=5,in=180] node[sloped,midway,scale=0.6,above]{Docker API calls} (4,1);
%
\draw[<->,thick,>=stealth] (app1.south) -- node[sloped,midway,scale=0.6,above]{UDP} (app2.north);
\draw[<->,thick,>=stealth] (app1.south) -- node[sloped,midway,scale=0.6,above]{UDP} (appn.north);
\draw[<->,thick,>=stealth] (app2.east) -- node[sloped,midway,scale=0.6,above]{UDP} (appn.west);
%
\draw (8.1,.75) node[below right,red,scale=0.8] {\textit{Java program}};
\draw (4.1,.75) node[below right,red,scale=0.8] {\textit{Java program}};
\end{tikzpicture}

### 2017-02-08 report/framework.tex
Fix figures and last typos

\section{EpToTester}
\label{sec:epto}
\sys is a framework using Docker and Docker Swarm. It is designed to ease the deployment of large scale distributed systems and in this particular case \jgroups and \epto. We use \sys to assess the claims made in \autocite{matos2015epto}. Although the implementation of \epto is written with benchmarking in mind, the code can be adapted for real applications with only minimal changes to the sources. We  use \sys instead of other solutions such as SPlay, which only supports LUA, as we need to test existing protocols written in different programming languages.
\subsection{Deployment}
\begin{figure}[htp]
	\centering
	\includegraphics[width=\linewidth]{figures/complete-architecture.pdf}
	\vspace{-2mm} 
	\caption[Caption]{\epto using the \sys framework\footnotemark}
	\vspace{-2mm} 
	\label{fig:complete-architecture}
\end{figure}
\mm{this needs to be explained in more detail in the text in particular the concept of different services, the benchmark, etc. the churn modules are also missing}
\footnotetext{This figure is partially inspired from a figure in \autocite{vaucher2016erasure}}
To deploy a protocol in our framework we need two different Docker Swarm services: one containing the tracker and one containing all replicas. We use two services to isolate the tracker from the peers. This lets us kill and add peers without having to worry about the tracker and also scale the tracker in case we need replication for load-balancing purposes. Both of these services use the same network overlay to communicate. This is achieved using Docker and especially the new Docker Swarm introduced in Docker 1.12. This lets us have a unified way of deploying our benchmarks locally or remotely on vastly different clusters with minimal modifications as well as a performant load-balancing of our nodes at no cost. Every benchmark is started through a Python script available on the master node. This script handles everything from starting benchmarks, scaling the cluster during a churn and collecting results through the framework Python module. Application, churn and cluster  parameters are customizable through YAML configuration files. Tracker and replica communication is up to the user. For example, \epto uses HTTP, while \jgroups uses TCP directly. Tracker implementation is also left to the user, although a REST Tracker implemented in Python is provided by default. The user can also opt to not use a tracker at all. \sys generates at least one log file per peer. Any important benchmarking information must be logged to a file to be later exploited.
Gradle\footnote{\href{https://gradle.org/}{https://gradle.org/}} is used to automate the project building. Finally, a script is provided to push the images to a repository accessible to the remote cluster and to push the benchmarking framework on the master node. \jgroups uses the same deployment method. Our framework applied to \epto can be seen in \autoref{fig:complete-architecture}.
\subsection{Fault Injection}
Our framework supports the ability to inject synthetic and real traces thanks to the work done in \autocite{vaucher2016erasure}. The synthetic churn provided by it was improved to support adding and removing nodes at the same time\mm{point out that when this is simultaneous it applies to different sets of nodes.}.

>>>>

\section{EpToTester}
\label{sec:epto}
\sys is a framework using Docker and Docker Swarm. It is designed to ease the deployment of large scale distributed systems and in this particular case \jgroups and \epto. We use \sys to assess the claims made in \autocite{matos2015epto}. Although the implementation of \epto is written with benchmarking in mind, the code can be adapted for real applications with only minimal changes to the sources. We  use \sys instead of other solutions such as SPlay, which only supports LUA, as we need to test existing protocols written in different programming languages.
\subsection{Deployment}
\begin{figure}[htp]
	\centering
	\includegraphics[width=\linewidth]{figures/complete-architecture.pdf}
	\vspace{-2mm} 
	\caption[Caption]{\epto using the \sys framework\footnotemark}
	\vspace{-2mm} 
	\label{fig:complete-architecture}
\end{figure}
\mm{this needs to be explained in more detail in the text in particular the concept of different services, the benchmark, etc. the churn modules are also missing}
\footnotetext{This figure is partially inspired from a figure in \autocite{vaucher2016erasure}}
To deploy a protocol in our framework we need two different Docker Swarm services: one containing the tracker and one containing all replicas. We use two services to isolate the tracker from the peers. This lets us kill and add peers without having to worry about the tracker and also scale the tracker in case we need replication for load-balancing purposes. Both of these services use the same network overlay to communicate. This is achieved using Docker and especially the new Docker Swarm introduced in Docker 1.12. This lets us have a unified way of deploying our benchmarks locally or remotely on vastly different clusters with minimal modifications as well as a performant load-balancing of our nodes at no cost. Every benchmark is started through a Python script available on the master node. This script handles everything from starting benchmarks, scaling the cluster during a churn and collecting results through the framework Python module. Application, churn and cluster  parameters are customizable through YAML configuration files. Tracker and replica communication is up to the user. For example, \epto uses HTTP, while \jgroups uses TCP directly. Tracker implementation is also left to the user, although a REST Tracker implemented in Python is provided by default. The user can also opt to not use a tracker at all. \sys generates at least one log file per peer. Any important benchmarking information must be logged to a file to be later exploited.
Gradle\footnote{\href{https://gradle.org/}{https://gradle.org/}} is used to automate the project building. Finally, a script is provided to push the images to a repository accessible to the remote cluster and to push the benchmarking framework on the master node. \jgroups uses the same deployment method. Our framework applied to \epto can be seen in \autoref{fig:complete-architecture}.
\subsection{Fault Injection}
Our framework supports the ability to inject synthetic and real traces thanks to the work done in \autocite{vaucher2016erasure}. The synthetic churn provided by it was improved to support adding and removing nodes at the same time. When removing and adding an equal amount of nodes, both instructions execute without canceling each other. \mm{point out that when this is simultaneous it applies to different sets of nodes.}.

### 2017-02-08 report/main.tex
Add figures as standalone pdfs and fix issues
*Issues were mentionned by Hugues
Fix more stuff pointed by Hugues
General comments.
Rework framework and background sections
Correct typos in report
Fix report based on Miguel's feedback
Fix figures and last typos

\usepackage[backend=biber,style=ieee,bibencoding=utf8,sorting=none,doi=false,isbn=false,url=false,date=short]{biblatex}
\usepackage{amssymb}
\usepackage[cmex10]{amsmath}
\usepackage{csquotes}
\usepackage[nolist]{acronym}
\usepackage{float}
\usepackage{todonotes}
\usepackage{pgfplots}
\usepackage{pgf}
\usepackage[binary-units]{siunitx}
\usepackage{pgfplotstable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage[hidelinks]{hyperref}
\usepackage{xspace}
\usepackage[caption=false]{subfig}

@@

\pgfplotscreateplotcyclelist{my colors}{%
solid, color=black\\%
densely dotted, color=blue\\%
densely dashed, color=red\\%
}
\makeatother
%% Environment for comments: Set the boolean to false to produce a comment-free version.
\newboolean{showcomments}
\setboolean{showcomments}{true}
\ifthenelse{\boolean{showcomments}}
{ \newcommand{\mynote}[3]{
		\fbox{\bfseries\sffamily\scriptsize#1}
		{\small$\blacktriangleright$\textsf{\textit{\color{#3}{#2}}}$\blacktriangleleft$}}}
{ \newcommand{\mynote}[3]{}}
% One command per author:
\newcommand{\jt}[1]{\mynote{Jocelyn}{#1}{blue}}
\newcommand{\hm}[1]{\mynote{Hugues}{#1}{orange}}

\newcommand{\epto}{\textsc{EpTO}\xspace}
\newcommand{\jgroups}{\textsc{JGroups}\xspace}

@@

\def\ieeetitle{EpTO TO DEFINE}
\def\ieeeauthor{X,X,X}

\def\thesistitle{EpTO TO DEFINE}
\def\thesissubtitle{X}
\def\thesisauthor{Jocelyn Thode}

@@

			\vspace{0.3in}
			{\Large Université de Fribourg \par}
			\vfill
			{\Large \today \par}

@@

		\end{center}
	\end{otherlanguage}
\end{titlepage}

@@

\input{abstract.tex}
\input{introduction.tex}
\input{ordering.tex}
\input{definitions.tex}
\input{framework.tex}
\input{evaluation.tex}
\input{future-work.tex}
\input{conclusion.tex}
\printbibliography
\end{document}

>>>>

\usepackage[backend=biber,style=ieee,bibencoding=utf8,sorting=none,doi=false,isbn=false,url=false,date=short]{biblatex}
\usepackage{amssymb}
\usepackage[cmex10]{amsmath}
\usepackage{csquotes}
\usepackage{cleveref}
\usepackage[nolist]{acronym}
\usepackage{float}
\usepackage{todonotes}
\usepackage{pgfplots}
\usepackage{pgf}
\usepackage[binary-units]{siunitx}
\usepackage{pgfplotstable}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\usepackage{xspace}
\usepackage[caption=false]{subfig}

@@

\pgfplotscreateplotcyclelist{my colors}{%
solid, color=black\\%
densely dotted, color=blue\\%
densely dashed, color=red\\%
}
\makeatother

%% Environment for comments: Set the boolean to false to produce a comment-free version.
\newboolean{showcomments}
\setboolean{showcomments}{false}
\ifthenelse{\boolean{showcomments}}
{ \newcommand{\mynote}[3]{
		\fbox{\bfseries\sffamily\scriptsize#1}
		{\small$\blacktriangleright$\textsf{\textit{\color{#3}{#2}}}$\blacktriangleleft$}}}
{ \newcommand{\mynote}[3]{}}
% One command per author:
\newcommand{\jt}[1]{\mynote{Jocelyn}{#1}{blue}}
\newcommand{\hm}[1]{\mynote{Hugues}{#1}{orange}}
\newcommand{\mm}[1]{\mynote{Miguel}{#1}{gray}}

\newcommand{\epto}{\textsc{EpTO}\xspace}
\newcommand{\jgroups}{\textsc{JGroups}\xspace}
\newcommand{\sys}{\textsc{LSDSuite}\xspace}

@@

\def\ieeetitle{EpTOTester}
\def\ieeeauthor{X,X,X}

\def\thesistitle{\epto}
\def\thesissubtitle{Implementation of a Large-Scale Epidemic Total Order Algorithm
}
\def\thesisauthor{Jocelyn Thode}

@@

			\vspace{0.3in}
			{\Large Université de Fribourg \par}
			\vfill

			\vspace{0.3in}
			{\Large \today \par}

@@

		\end{center}

	\pagebreak

	\section*{Abstract}

	\noindent 
	\epto is one of the recently introduced total order algorithms for large-scale distributed systems, and provides total order and scalability at the same time. In this paper, we verify this claim by designing a framework to facilitate the evaluation of large scale distributed systems, implement \epto and evaluate its reliability in real-world conditions by comparing it to a deterministic total order algorithm provided by the \jgroups toolkit. We first compare them in a perfect environment assessing the scalability in terms of events throughput and number of peers. We then compare them using a synthetic churn trace and a real one using the same metrics. 
	Our results show \epto is performing as expected, even though in the system sizes we tested \jgroups is still more efficient in a stable environment.
	By extrapolating our results for larger system sizes we can clearly see that \jgroups starts to degrade with the system size. 
	Still, further testing on a bigger cluster is required to evaluate how \epto performs when \jgroups is no longer able to keep up with scale.

	\bigskip

	Dr Hugues Mercier, Institutes of Computer Science and Mathematics, University of Neuchâtel, Supervisor

	Dr Miguel Matos, HASLab - INESC TEC \&, University of Minho, Portugal,  Co-supervisor

	\end{otherlanguage}
\end{titlepage}

@@

\input{abstract.tex}
\input{introduction.tex}
\input{definitions.tex}
\input{background.tex}
\input{framework.tex}
\input{evaluation.tex}
\input{future-work.tex}
\input{conclusion.tex}

\printbibliography

\end{document}
